The problem and promise of scale in multilayer animal social networks

### 2020-09-18 paper/manuscript.Rmd
fix title
minor edits

---
title: The problem and promise of scale in animal social multilayer networks
author:
  - name: Alec L. Robitaille
    email: robit.alec@gmail.com
    institute: bio
    correspondence: true
  - name: Quinn M.R. Webber
    institute: cabe
  - name: Julie W. Turner
    institute: bio
  - name: Eric Vander Wal
    institute: [bio, cabe]
institute: 
  - bio: Department of Biology, Memorial University of Newfoundland, Canada
  - cabe: Cognitive and Behavioural Ecology Interdisciplinary Program, Memorial University of Newfoundland 
output:
   bookdown::word_document2:
     reference_docx: template.docx
     pandoc_args:
      - '--lua-filter=scholarly-metadata.lua'
      - '--lua-filter=author-info-blocks.lua'
knit: (function(inputFile, encoding) {
  rmarkdown::render(input = inputFile, encoding = encoding, output_format = "all") })
bibliography: ../references/knitcite.bib
csl: csl.csl
---

@@

(ref:spacetime) Space-time diagram representing variation the relative spatial and temporal extent required for different types of social and communication processes for four species, including spotted hyaena, passerine birds, sleepy lizards, and elephants. Spatial and temporal extent for social interactions, e.g. mating, grooming, or aggression, are similar for most species because physical contact between two individuals is required for many social interactions. The logical extension is that spatial and temporal extent for social interaction is hierarchically nested within the spatial and temporal extent for social association because individuals must share space to interact. By contrast, different species have potential for greater spatial and temporal extents, for example, temporal extent for vocal communication is similar for most species because most vocal calls only persist in the environment for seconds, but spatial extent for vocal communication is highly variable with elephant calls extending the great distance and passerine calls extending the shortest distance.

@@

### Network layer construction
We generated proximity-based social networks using the R package `spatsoc`
[@Robitaille_2019] in `r substr(version$version.string, 1, 15)` [@R_Core_Team]. 
Typically for ungulates and other gregarious
mammals, the ‘chain rule’ is used for group assignment [@Croft_2008; @Kasozi_2020]. 
The chain rule is applied by assigning a group identifier to the union of
buffered GPS fixes collected at each two hour time step. As such, individuals in a group are within
the social distance threshold of at least one other though not necessarily all
other individuals [@Robitaille_2019]. Group assignment is defined using a 
temporal threshold of 5 minutes
and a social distance threshold of 50 m [@Peignier_2019; @Lesmerises_2018]. 
In all networks, individual caribou were represented as nodes and associations between
individuals were represented as edges. We weighted edges by the strength of 
association between individuals using the simple ratio index [SRI, @Cairns_1987].

>>>>

---
title: The problem and promise of scale in multilayer animal social networks
author:
  - name: Alec L. Robitaille
    email: robit.alec@gmail.com
    institute: bio
    correspondence: true
  - name: Quinn M.R. Webber
    institute: cabe
  - name: Julie W. Turner
    institute: bio
  - name: Eric Vander Wal
    institute: [bio, cabe]
institute: 
  - bio: Department of Biology, Memorial University of Newfoundland, Canada
  - cabe: Cognitive and Behavioural Ecology Interdisciplinary Program, Memorial University of Newfoundland 
output:
   bookdown::word_document2:
     reference_docx: template.docx
     pandoc_args:
      - '--lua-filter=scholarly-metadata.lua'
      - '--lua-filter=author-info-blocks.lua'
knit: (function(inputFile, encoding) {
  rmarkdown::render(input = inputFile, encoding = encoding, output_format = "all") })
bibliography: ../references/knitcite.bib
csl: csl.csl
---

@@

(ref:spacetime) Space-time diagram representing variation the relative spatial and temporal extent required for different types of social and communication processes for four species, including spotted hyenas, passerine birds, sleepy lizards, and elephants. Spatial and temporal extent for social interactions, e.g. mating, grooming, or aggression, are similar for most species because physical contact between two individuals is required for many social interactions. The logical extension is that spatial and temporal extent for social interaction is hierarchically nested within the spatial and temporal extent for social association because individuals must share space to interact. By contrast, different species have potential for greater spatial and temporal extents, for example, temporal extent for vocal communication is similar for most species because most vocal calls only persist in the environment for seconds, but spatial extent for vocal communication is highly variable with elephant calls extending the great distance and passerine calls extending the shortest distance.

@@

### Network layer construction
We generated proximity-based social networks using the R package `spatsoc`
[@Robitaille_2019] in `r substr(version$version.string, 1, 15)` [@R_Core_Team]. 
Typically for ungulates and other gregarious
mammals, the ‘chain rule’ is used for group assignment [@Croft_2008; @Kasozi_2020]. 
The chain rule is applied by assigning a group identifier to the union of
buffered GPS fixes collected at each two hour time step. As such, individuals in a group are within
the social distance threshold of at least 1 other individual, though not 
necessarily all other individuals [@Robitaille_2019]. Group assignment is defined using a 
temporal threshold of 5 minutes
and a social distance threshold of 50 m [@Peignier_2019; @Lesmerises_2018]. 
In all networks, individual caribou were represented as nodes and associations between
individuals were represented as edges. We weighted edges by the strength of 
association between individuals using the simple ratio index [SRI, @Cairns_1987].
